\textbf{Transparency to hybrid open access through publisher-provided metadata: An article-level study of Elsevier}

### 2021-05-02 analysis/manuscript.Rmd
starting revision

```{r, rev_flipped}
flipped_jns <- els_jns %>%
  distinct(issn, oa_model) %>%
  group_by(issn) %>%
  filter(n() > 1)
flipped_jns_ind <- els_jns %>%
  filter(issn %in% flipped_jns$issn) %>%
  group_by(issn) %>%
  slice(which.max(year)) %>%
  ungroup() %>%
  count(oa_model)
```
```{r hybrid_oa_per_year}
# journal and article metrics **per year**
hybrid_oa_per_year <- hybrid_oa_volume %>%
  group_by(issued_year) %>%
  # distinct jns with at least one article per year
  filter(oa > 0) %>%
  summarise(
      # distinct jns with at least one article per year
    n_journals = n(),
    # article metrics
    articles_n = sum(articles),
    articles_mean = mean(articles),
    articles_sd = sd(articles),
    # oa articles metrics
    oa_n = sum(oa),
    oa_mean = mean(oa),
    oa_sd = sd(oa)
    ) %>%
  mutate(oa_uptake = oa_n / articles_n)
# oa uptake per year
oa_uptake_per_year <- hybrid_oa_volume %>% 
  filter(oa > 0) %>%
  mutate(prop = oa / articles) %>%
  group_by(issued_year) %>%
  summarise(oa_uptake_mean = mean(prop),
            oa_uptake_sd = sd(prop))
# merge indicators
ind_per_year <- inner_join(hybrid_oa_per_year, oa_uptake_per_year, by = "issued_year")

>>>>

```{r, rev_flipped}
flipped_jns <- els_jns %>%
  distinct(issn, oa_model) %>%
  group_by(issn) %>%
  filter(n() > 1)
flipped_jns_ind <- els_jns %>%
  filter(issn %in% flipped_jns$issn) %>%
  group_by(issn) %>%
  slice(which.max(year)) %>%
  ungroup() %>%
  count(oa_model)
```

```{r hybrid_oa_per_year}
# journal and article metrics **per year**
hybrid_oa_per_year <- hybrid_oa_volume %>%
  group_by(issued_year) %>%
  # distinct jns with at least one article per year
  filter(oa > 0) %>%
  summarise(
      # distinct jns with at least one article per year
    n_journals = n(),
    # article metrics
    articles_n = sum(articles),
    articles_mean = mean(articles),
    articles_sd = sd(articles),
    # oa articles metrics
    oa_n = sum(oa),
    oa_mean = mean(oa),
    oa_sd = sd(oa)
    ) %>%
  mutate(oa_uptake = oa_n / articles_n)
# oa uptake per year
oa_uptake_per_year <- hybrid_oa_volume %>% 
  filter(oa > 0) %>%
  mutate(prop = oa / articles) %>%
  group_by(issued_year) %>%
  summarise(oa_uptake_mean = mean(prop),
            oa_uptake_sd = sd(prop))
# merge indicators
ind_per_year <- inner_join(hybrid_oa_per_year, oa_uptake_per_year, by = "issued_year")
